---
title: "Retrospective Cohort Study of Outcomes for Neonates and Infants Undergoing Inguinal Hernia Surgery at Multiple Australian and New Zealand Hospitals: The RetroNeo Study." 
subtitle: "Statistical Analysis"
author: "Dr Benjamin Moran, MBBS, BMedSci (Hons), MMedStats, FCICM, FANZCA"
date: today
format:   
  html:
    embed-resources: true
    grid: 
      body-width: 1000px
      sidebar-width: 200px
      margin-width: 100px
      gutter-width: 0.5rem
execute:
  cache: true
toc: true
toc-location: left
toc-depth: 5
number-sections: true
theme: yeti
---


## Introduction
This is the statistical analysis that accompanies the RetroNeo study, which examines the anaesthetic techniques and perioperative outcomes of neonates and infants undergoing inguinal hernia surgery.

## Results
```{r, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(gt)
library(gtsummary)

# knitr options
knitr::opts_chunk$set(echo = F, message = F, warning = F, error = T, out.width = "90%", dev = "png", dpi = 300, cache = T)

#==========================================TABLE 1: DEMOGRAPHICS==========================================#

# Import data
load("retro_wrangled.RData")

# Source functions
source("Functions.r")

# Generate Table 1 (with removed subsequent surgeries)
retro_tbl <- retro |> 
  filter(second_surg_index == 0)

tbl_dem <- retro_tbl |>  
  select(age_pma_wks, dem_sex, dem_wgt, dem_loc, resp_support_prior, mhx_nicu, mhx_iugr, mhx_ivh, mhx_retin, mhx_ccd, mhx_cld, mhx_apn, mhx_intu, mhx_rsp, mhx_caff,  age_cat) |>  
    tbl_summary(by = age_cat, missing = "no",
            label = list(
              age_pma_wks = "Post-Menstrual Age at Birth in Weeks (Median (IQR))",
              dem_sex = "Male Sex (N (%))",
              dem_wgt = "Weight at Birth in Grams (Median (IQR))",
              dem_loc = "Location Prior to Day of Surgery",
              mhx_nicu = "NICU Admission Between Birth & Surgery",
              mhx_iugr = "Intrauterine Growth Restriction (IUGR)",
              mhx_ivh = "Intraventricular Haemorrhage (IVH)",
              mhx_retin = "Retinopathy of Prematurity",
              mhx_ccd = "Congenital Cardiac Disease",
              mhx_cld = "Chronic Lung Disease",
              mhx_apn = "History of Apnoea (Any Aetiology)",
              mhx_intu = "History of Invasive Ventilation",
              mhx_rsp = "Respiratory Support at Surgery",
              mhx_caff = "History of Caffeine Use",
              resp_support_prior = "Respiratory Support Prior to Surgery"),
            value = list(
              dem_sex ~ 1,
              mhx_nicu ~ 1,
              mhx_iugr ~ 1,
              mhx_ivh ~ 1,
              mhx_retin ~ 1,
              mhx_ccd ~ 1,
              mhx_cld ~ 1,
              mhx_apn ~ 1,
              mhx_intu ~ 1,
              mhx_rsp ~ 1,
              mhx_caff ~ 1),
            statistic = list(
              dem_sex ~ "{n} ({p}%)"
              ))|> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  add_overall() |> 
  bold_labels() |> 
  italicize_labels() |>
  remove_row_type(resp_support_prior,type = "level", level_value = "None") |> 
  as_gt() |> 
    tab_row_group(
      label = md("***Medical History***"),
      rows = 17:25
  ) |> 
    row_group_order(groups = c(NA, "***Medical History***")) |> 
    tab_style(
      style = cell_fill(color = "gray95"),
      locations = cells_row_groups(groups = "***Medical History***")
  ) |> 
    tab_style(
    style = cell_text(align = "left", indent = px(20)),
    locations = cells_body(columns = everything(),
    rows = 17:25)
  )
```

### Demographics

```{r, message=FALSE, warning=FALSE, echo = F}
tbl_dem
```


```{r, include=FALSE, warning=FALSE, message=FALSE}
#==========================================TABLE 2: SURGERY==========================================#
tbl_surg <- retro_tbl |>  
  select(age_pma_wks, age_pma_surg_wks, dem_wgt, sur_wgt, sur_hernia, sur_type, sur_incarc, surgeries_in_group, sur_asspro, total_dur, anaes_dur, surg_dur, pacu, pacu_dur, age_cat) |>  
    tbl_summary(by = age_cat, missing = "no",
            label = list(
              age_pma_wks = "Post-Menstrual Age at Birth in Weeks (Median (IQR))",
              age_pma_surg_wks = "Post-Menstrual Age at Surgery in Weeks (Median (IQR))",
              dem_wgt = "Median Weight at Birth (Grams)",
              sur_wgt = "Median Weight at Surgery (Grams)",
              sur_hernia = "Type of Hernia Repair",
              sur_type = "Surgical Approach",
              sur_incarc = "Incarcerated Hernia",
              surgeries_in_group = "Number of Surgeries in Index Admission",
              sur_asspro = "Additional Associated Procedure",
              total_dur = "Median Total Duration (Mins)",
              anaes_dur = "Median Anaesthetic Duration (Mins)",
              surg_dur = "Median Surgical Duration (Mins)",
              pacu = "Transferred to PACU",
              pacu_dur = "Median Time Duration in PACU (Mins)"),
            value = list(
              sur_incarc ~ 1,
              sur_asspro ~ 1,
              pacu ~ "Yes"))|> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  add_overall() |> 
  bold_labels() |> 
  italicize_labels()
```

### Surgical Details

```{r, message=FALSE, warning=FALSE, echo = F}
tbl_surg
```


```{r, include=FALSE, warning=FALSE, message=FALSE}
#==========================================TABLE 3: ANAESTHETICS==========================================#
# Calculate the TRUE overall N for each age category across ALL strata
overall_age_n <- retro |>
  dplyr::count(age_cat) |>
  tidyr::pivot_wider(names_from = age_cat, values_from = n) |> 
  dplyr::mutate(Overall = sum(`≤ 27 Weeks`, `28-32 Weeks`, `33-36 Weeks`, `≥37 Weeks`))

# Anaesthetic Type Tables
tbl_ga_all <- tbl_ga_fn(anaes_group = "all")
tbl_ga_ga <- tbl_ga_fn(anaes_group = "GA")
tbl_ga_spinal <- tbl_ga_fn(anaes_group = "Spinal")
tbl_ga_caudal <- tbl_ga_fn(anaes_group = "Caudal")

# Intraop Analgesia
tbl_ga_intraop_analg <- tbl_intraop_analg_fn("GA Only")
tbl_ga_caud_intraop_analg <- tbl_intraop_analg_fn("GA + Caudal")
tbl_ga_spi_intraop_analg <- tbl_intraop_analg_fn("GA + Spinal")
tbl_spi_intraop_analg <- tbl_intraop_analg_fn("Spinal Only")
tbl_spi_sed_intraop_analg <- tbl_intraop_analg_fn("Spinal + Sedation")
tbl_caud_intraop_analg <- tbl_intraop_analg_fn("Caudal Only")
tbl_caud_sed_intraop_analg <- tbl_intraop_analg_fn("Caudal + Sedation")

# Stack Tables
tbl_intraop_analg <- tbl_stack(
  tbls = list(tbl_ga_intraop_analg, tbl_ga_caud_intraop_analg, tbl_ga_spi_intraop_analg, tbl_spi_intraop_analg, tbl_spi_sed_intraop_analg, tbl_caud_intraop_analg, tbl_caud_sed_intraop_analg)) |> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  modify_spanning_header(stat_0 ~ NA) |> 
  modify_footnote(everything() ~ NA) |> 
  modify_header(
    label ~ "**Anaesthetic Type**",
    stat_1 ~ paste0("**≤ 27 Weeks**", "<br>", "N = ", overall_age_n$`≤ 27 Weeks`),
    stat_2 ~ paste0("**28-32 Weeks**", "<br>", "N = ", overall_age_n$`28-32 Weeks`),
    stat_3 ~ paste0("**33-36 Weeks**", "<br>", "N = ", overall_age_n$`33-36 Weeks`),
    stat_4 ~ paste0("**≥37 Weeks**", "<br>", "N = ", overall_age_n$`≥37 Weeks`),
    stat_0 ~ paste0("**Overall**", "<br>", "N = ", nrow(retro))) |> 
  modify_table_body(
    ~ .x |>
      dplyr::mutate(
        across(starts_with("stat_"), ~ stringr::str_replace_all(., "^0 \\(.*\\)$", "0")))) |> 
  as_gt() |>
  gt::tab_style(
    style = gt::cell_fill(color = "grey80"),
    locations = gt::cells_body(
      rows = c(1, 5, 9, 13, 17, 21, 25)))


tbl_spinal <- retro |>  
  filter(spinal == "1") |> 
  mutate(
    spinal_drug_conc_comb = paste(spinal_drug, spinal_drug_conc, sep = " "),
    spinal_drug_conc_comb = case_when(str_detect(spinal_drug_conc_comb, "NA") ~ "Unknown",
                                      .default = spinal_drug_conc_comb),
    spinal_drug_conc_comb = factor(spinal_drug_conc_comb, levels = c("Bupivacaine 0.25%", "Bupivacaine 0.5%", "Levobupivacaine 0.5%", "Levobupivacaine 0.7%", "Ropivacaine 0.2%", "Unknown"))) |> 
  select(spinal_drug_conc_comb, spinal_attempts, spinal_complications, spinal_ga_conv, sedation, sed_prop, sed_dexmede, sed_no2, sed_sucrose, airway_type,  age_cat) |>  
    tbl_summary(by = age_cat, missing = "no",
            label = list(
              spinal_drug_conc_comb = "Spinal Local Anaesthetic (Drug (Concentration))",
              spinal_attempts = "Number of Attempts",
              spinal_complications = "Complications",
              spinal_ga_conv = "Conversion to GA",
              sedation = "Adjuvant Sedation Used",
              sed_prop = "Propofol Sedation",
              sed_dexmede = "Dexmedetomidine Sedation",
              sed_no2 = "NO2",
              sed_sucrose = "Sucrose",
              airway_type = "Type of Airway"),
            value = list(
              sedation ~ 1,
              sed_prop ~ 1,
              sed_dexmede ~ 1,
              sed_no2 ~ 1,
              sed_sucrose ~ 1,
              spinal_ga_conv ~ 1))|> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  add_overall() |> 
  bold_labels() |> 
  italicize_labels() |>     
  modify_table_body(
      ~ .x |>
        dplyr::mutate(
          across(starts_with("stat_"), ~ stringr::str_replace_all(., "^0 \\(.*\\)$", "0"))))

tbl_caudal <- retro |>  
  filter(caudal == "1") |> 
  mutate(
    caudal_drug_conc_comb = paste(caudal_drug, caudal_drug_conc, sep = " "),
    caudal_drug_conc_comb = case_when(str_detect(caudal_drug_conc_comb, "NA") ~ "Unknown",
                                      .default = caudal_drug_conc_comb),
    caudal_drug_conc_comb = factor(caudal_drug_conc_comb, levels = c("Bupivacaine 0.25%", "Bupivacaine 0.5%","Levobupivacaine 0.2%", "Levobupivacaine 0.25%", "Ropivacaine 0.1%", "Ropivacaine 0.2%", "Ropivacaine 0.3%", "Unknown")),
    caudal_attempts = na_if(caudal_attempts, "0"),
    caudal_attempts = na_if(caudal_attempts, "99"),
    caudal_attempts = na_if(caudal_attempts, "9999"),
    caudal_sed_type = case_when(
      sed_dexmede == "1" & sed_prop == "0" ~ "Dexmedetomidine",
      #sed_dexmede == "0" & sed_prop == "1" ~ "Propofol",
      sed_dexmede == "1" & sed_prop == "1" ~ "Dexmedetomidine + Propofol"),
    caudal_sed_type = factor(sed_type, levels = c("Dexmedetomidine", "Propofol", "Dexmedetomidine + Propofol")),
    anaes_type2 = anaes_type) |> 
  select(caudal_drug_conc_comb, caudal_add, caudal_attempts,  anaes_type, sedation, caudal_sed_type, anaes_type2, caudal_complications, caudal_ga_conv, sed_sucrose, airway_type, age_cat) |>  
    tbl_summary(by = age_cat, missing = "no",
            label = list(
              caudal_drug_conc_comb = "Spinal Local Anaesthetic (Concentration)",
              caudal_add = "Caudal Additives",
              caudal_attempts = "Number of Attempts",
              caudal_complications = "Complications",
              caudal_ga_conv = "Conversion to GA",
              anaes_type = "GA with Caudal",
              sedation = "Adjuvant Sedation Used",
              caudal_sed_type = "Type of Sedation (% of Those with Sedation)",
              anaes_type2 = "Caudal Only",
              sed_sucrose = "Sucrose",
              airway_type = "Type of Airway"),
            value = list(
              sedation ~ 1,
              sed_sucrose ~ 1,
              caudal_ga_conv ~ 1,
              anaes_type ~ "GA + Caudal",
              anaes_type2 ~ "Caudal Only"))|> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  add_overall() |> 
  bold_labels() |> 
  italicize_labels() |> 
  modify_table_body(
      ~ .x |>
        dplyr::mutate(
          across(starts_with("stat_"), ~ stringr::str_replace_all(., "^0 \\(.*\\)$", "0"))))

# Secondary Anaesthetic Table
tbl_sec <- retro |> 
  filter(sec_anaes == "1") |> 
  select(anaes_type, reason_sec_anaes, sec_ga, sec_spinal, sec_caudal, sec_sed, age_cat) |> 
  tbl_summary(by = age_cat, missing = "no",
            label = list(
              anaes_type = "Primary Anaesthetic",
              reason_sec_anaes = "Reason for Secondary Anaesthetic",
              sec_ga = "Secondary GA",
              sec_spinal = "Secondary Spinal",
              sec_caudal = "Secondary Caudal",
              sec_sed = "Secondary Sedation"),
            value = list(
              sec_ga ~ 1,
              sec_spinal ~ 1,
              sec_caudal ~ 1,
              sec_sed ~ 1))|> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  add_overall() |> 
  bold_labels() |> 
  italicize_labels() |> 
  modify_table_body(
      ~ .x |>
        dplyr::mutate(
          across(starts_with("stat_"), ~ stringr::str_replace_all(., "^0 \\(.*\\)$", "0"))))

```

### Intraoperative

#### Details of Anaesthesia

::: panel-tabset
## Overall
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_ga_all
```
## GA-Based
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_ga_ga
```

## Spinal-Based
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_ga_spinal
```

## Caudal-Based
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_ga_caudal
```

## Spinal
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_spinal
```

## Caudal
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_caudal
```

## Intraoperative Analgesia
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_intraop_analg
```

## Secondary Anaesthetic
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_sec
```

## Anaesthetic Type: Graph
```{r, message=FALSE, warning=FALSE, include=FALSE}
# Plot
plot_anaes_type_overall <- retro |> 
  dplyr::filter(!anaes_type %in% c("GA + Spinal + Caudal", "GA + Caudal + Sedation", NA)) |> 
  group_by(anaes_type) |> 
  summarise(num = n()) |>  
  mutate(perc = num*100/sum(num)) |> 
  mutate(perc = round(perc, 1)) |> 
ggplot(aes(x = anaes_type, y = perc, fill = anaes_type))+
  geom_col(position = "dodge")+
  theme_bw()+
  guides(fill="none")+
  geom_text(aes(label = paste0(perc, "%")),
            position = position_dodge(width = .9),
            vjust = -0.7,
            size = 3)+
  labs(y = "Percent (%)", x = "Anaesthetic Type", title = "Anaesthetic Type", subtitle = "For All Age Categories",
       fill = "Age Categories at Birth")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_fill_brewer(palette = "Blues", direction = -1)+
  coord_cartesian(ylim=c(0,100))
```

```{r, message=FALSE, warning=FALSE, echo = F}
plot_anaes_type_overall
```

## Anaesthetic Type: By Age
```{r, message=FALSE, warning=FALSE, include=FALSE}
# Plot
plot_anaes_type_age <- retro |> 
  dplyr::filter(!anaes_type %in% c("Caudal Only", "GA + Spinal + Caudal", "GA + Caudal + Sedation", NA)) |> 
  group_by(age_cat, anaes_type) |> 
  summarise(num = n()) |>  
  mutate(perc = num*100/sum(num)) |> 
  mutate(perc = round(perc, 1)) |> 
ggplot(aes(x = anaes_type, y = perc,  fill= age_cat))+
  geom_col(position = "dodge")+
  theme_bw()+
  geom_text(aes(label = paste0(perc, "%")),
            position = position_dodge(width = .9),
            vjust = -0.7,
            size = 1.8)+
  labs(y = "Percent (%)", x = "Anaesthetic Type", title = "Anaesthetic Type", subtitle = "By Age Categories",
       fill = "Age Categories at Birth")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_fill_brewer(palette = "Blues", direction = -1)+
  coord_cartesian(ylim=c(0,100))
```

```{r, message=FALSE, warning=FALSE, echo = F}
plot_anaes_type_age
```

## Airway Type: Overall
```{r, message=FALSE, warning=FALSE, include = FALSE}
plot_airway_overall <- retro |> 
  filter(anaes_type %in% c("GA Only", "GA + Spinal", "GA + Caudal")) |> 
  filter(airway_type != "None") |> 
  group_by(airway_type) |> 
  summarise(num = n()) |>  
  mutate(perc = num*100/sum(num)) |> 
  mutate(perc = round(perc, 1)) |> 
ggplot(aes(x = airway_type, y = perc, fill= airway_type))+
  geom_col(position = "dodge")+
  theme_bw()+
  guides(fill="none")+
  geom_text(aes(label = paste0(perc, "%")),
            position = position_dodge(width = .9),
            vjust = -0.7,
            size = 3)+
  labs(y = "Percent (%)", x = "Airway", title = "Airway Type in Patients Receiving GA", subtitle = "For All Age Categories")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_fill_brewer(palette = "Gn", direction = -1)+
  coord_cartesian(ylim=c(0,100))
```

```{r, message=FALSE, warning=FALSE, echo = F}
plot_airway_overall
```

## Airway Type: By Age
```{r, include=FALSE, warning=FALSE, message=FALSE}
plot_airway_age <- retro |> 
  filter(anaes_type %in% c("GA Only", "GA + Spinal", "GA + Caudal")) |> 
  filter(airway_type != "None") |> 
  group_by(age_cat, airway_type) |> 
  summarise(num = n()) |>  
  mutate(perc = num*100/sum(num)) |> 
  mutate(perc = round(perc, 1)) |> 
ggplot(aes(x = airway_type, y = perc, fill= age_cat))+
  geom_col(position = "dodge")+
  theme_bw()+
  geom_text(aes(label = paste0(perc, "%")),
            position = position_dodge(width = .9),
            vjust = -0.7,
            size = 2)+
  labs(y = "Percent (%)", x = "Airway", title = "Airway Type in Patients Receiving GA", subtitle = "By Age Categories",
       fill = "Age Categories")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_fill_brewer(palette = "Gn", direction = -1)+
  coord_cartesian(ylim=c(0,100))
```

```{r, message=FALSE, warning=FALSE, echo = F}
plot_airway_age
```
:::


#### Complications
Overall, there were 65 patients that had an intraoperative complication, with 73 separate complication events.
```{r, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}

# Number of complications per anaesthetic type
tbl_overall_intraop_compl <- tbl_compl_fn("All")
tbl_ga_intraop_compl <- tbl_compl_fn("GA Only")
tbl_ga_caud_intraop_compl <- tbl_compl_fn("GA + Caudal")
tbl_ga_spi_intraop_compl <- tbl_compl_fn("GA + Spinal")
tbl_spi_intraop_compl <- tbl_compl_fn("Spinal Only")
tbl_spi_sed_intraop_compl <- tbl_compl_fn("Spinal + Sedation")
tbl_caud_intraop_compl <- tbl_compl_fn("Caudal Only")
tbl_caud_sed_intraop_compl <- tbl_compl_fn("Caudal + Sedation")

# Stack Tables
tbl_number_intraop_compl <- tbl_stack(
  tbls = list(tbl_overall_intraop_compl,tbl_ga_intraop_compl, tbl_ga_caud_intraop_compl, tbl_ga_spi_intraop_compl, tbl_spi_intraop_compl, tbl_spi_sed_intraop_compl, tbl_caud_intraop_compl, tbl_caud_sed_intraop_compl)) |> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  modify_spanning_header(stat_0 ~ NA) |> 
  modify_footnote(everything() ~ NA) |> 
  modify_header(label ~ "**Anaesthetic Type**") |> 
  modify_table_body(
    ~ .x |>
      dplyr::mutate(
        across(starts_with("stat_"), ~ stringr::str_replace_all(., "^0 \\(.*\\)$", "0")))) |> 
  as_gt() |>
  gt::tab_style(
    style = gt::cell_fill(color = "grey80"),
    locations = gt::cells_body(rows = 1)) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(rows = 1))

# Type of Complications by anaesthetic type
tbl_overall_intraop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_intraop_", 1:3),
  strata = "Overall",
  label = "Overall")

tbl_ga_intraop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_intraop_", 1:3),
  strata = "GA Only",
  label = "GA Only",
  add_n_to_label = TRUE)

tbl_ga_caud_intraop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_intraop_", 1:3),
  strata = "GA + Caudal",
  label = "GA + Caudal",
  add_n_to_label = TRUE)

# GA + Spinal- no complications

tbl_spinal_intraop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_intraop_", 1:3),
  strata = "Spinal Only",
  label = "Spinal Only",
  add_n_to_label = TRUE)

# Spinal + Sedation- no complications

# Caudal Only- no complications

tbl_caud_sed_intraop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_intraop_", 1:3),
  strata = "Caudal + Sedation",
  label = "Caudal + Sedation",
  add_n_to_label = TRUE)

# Stack Tables
tbl_intraop_compl_type <- tbl_stack(
  tbls = list(tbl_overall_intraop_compl, tbl_ga_intraop_compl, tbl_ga_caud_intraop_compl, tbl_spinal_intraop_compl, tbl_caud_sed_intraop_compl)) |> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  modify_spanning_header(stat_0 ~ NA) |> 
  modify_footnote(everything() ~ NA) |> 
  modify_header(
    label ~ "**Anaesthetic Type**",
    stat_1 ~ paste0("**≤ 27 Weeks**", "<br>", "N = ", overall_age_n$`≤ 27 Weeks`),
    stat_2 ~ paste0("**28-32 Weeks**", "<br>", "N = ", overall_age_n$`28-32 Weeks`),
    stat_3 ~ paste0("**33-36 Weeks**", "<br>", "N = ", overall_age_n$`33-36 Weeks`),
    stat_4 ~ paste0("**≥37 Weeks**", "<br>", "N = ", overall_age_n$`≥37 Weeks`),
    stat_0 ~ paste0("**Overall**", "<br>", "N = ", nrow(retro))) |> 
  as_gt() |>
  gt::tab_style(
    style = gt::cell_fill(color = "grey80"),
    locations = gt::cells_body(
      rows = c(1, 7, 13, 19, 23)))


# Complication Interventions
# Generate Overall Row
tbl_overall_intraop_compl_int <- tbl_overall_intraop_compl |> 
  remove_row_type(complication_type, type = "level")

# By Complication Type
tbl_brady_intraop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("brd_int_intraop_", 1:3),
  strata = "Overall",
  label = "Bradycardia",
  intervention = TRUE)

tbl_hypo_intraop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("hypo_int_intraop_", 1:3),
  strata = "Overall",
  label ="Hypotension",
  intervention = TRUE)

tbl_apn_intraop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("apn_int_intraop_", 1:3),
  strata = "Overall",
  label = "Apnoea",
  intervention = TRUE)

tbl_des_intraop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("des_int_intraop_", 1:3),
  strata = "Overall",
  label = "Desaturation",
  intervention = TRUE)

# Bronchospasm- no intervention

tbl_lar_intraop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("lar_int_intraop_", 1:3),
  strata = "Overall",
  label = "Larngospasm",
  intervention = TRUE)

# Stack Tables
tbl_intraop_compl_int <- tbl_stack(
  tbls = list(tbl_overall_intraop_compl_int, tbl_brady_intraop_compl, tbl_hypo_intraop_compl, tbl_apn_intraop_compl, tbl_des_intraop_compl, tbl_lar_intraop_compl), quiet = TRUE) |> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  modify_spanning_header(stat_0 ~ NA) |> 
  modify_footnote(everything() ~ NA) |> 
  modify_header(
    label ~ "**Complication Type & Intervention**",
    stat_1 ~ paste0("**≤ 27 Weeks**", "<br>", "N = ", overall_age_n$`≤ 27 Weeks`),
    stat_2 ~ paste0("**28-32 Weeks**", "<br>", "N = ", overall_age_n$`28-32 Weeks`),
    stat_3 ~ paste0("**33-36 Weeks**", "<br>", "N = ", overall_age_n$`33-36 Weeks`),
    stat_4 ~ paste0("**≥37 Weeks**", "<br>", "N = ", overall_age_n$`≥37 Weeks`),
    stat_0 ~ paste0("**Overall**", "<br>", "N = ", nrow(retro))) |> 
  as_gt() |>
  gt::tab_style(
    style = gt::cell_fill(color = "grey75"),
    locations = gt::cells_body(
      rows = c(1))) |> 
  gt::tab_style(
    style = gt::cell_fill(color = "grey90"),
    locations = gt::cells_body(
      rows = c(2, 6, 12, 20, 26)))
```

::: panel-tabset
## Number of Complications
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_number_intraop_compl
```

## Complication Type
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_intraop_compl_type
```

## Interventions
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_intraop_compl_int
```
:::


```{r, include=FALSE, warning=FALSE, message=FALSE}
#==========================================TABLE 4: POST-OPERATIVE==========================================#

# Postop Analgesia
tbl_ga_postop_analg <- tbl_postop_analg_fn("GA Only")
tbl_ga_caud_postop_analg <- tbl_postop_analg_fn("GA + Caudal")
tbl_ga_spi_postop_analg <- tbl_postop_analg_fn("GA + Spinal")
tbl_spi_postop_analg <- tbl_postop_analg_fn("Spinal Only")
tbl_spi_sed_postop_analg <- tbl_postop_analg_fn("Spinal + Sedation")
tbl_caud_postop_analg <- tbl_postop_analg_fn("Caudal Only")
tbl_caud_sed_postop_analg <- tbl_postop_analg_fn("Caudal + Sedation")

# Stack Tables
tbl_postop_analg <- tbl_stack(
  tbls = list(tbl_ga_postop_analg, tbl_ga_caud_postop_analg, tbl_ga_spi_postop_analg, tbl_spi_postop_analg, tbl_spi_sed_postop_analg, tbl_caud_postop_analg, tbl_caud_sed_postop_analg)) |> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  modify_spanning_header(stat_0 ~ NA) |> 
  modify_footnote(everything() ~ NA) |> 
  modify_header(
    label ~ "**Anaesthetic Type**",
    stat_1 ~ paste0("**≤ 27 Weeks**", "<br>", "N = ", overall_age_n$`≤ 27 Weeks`),
    stat_2 ~ paste0("**28-32 Weeks**", "<br>", "N = ", overall_age_n$`28-32 Weeks`),
    stat_3 ~ paste0("**33-36 Weeks**", "<br>", "N = ", overall_age_n$`33-36 Weeks`),
    stat_4 ~ paste0("**≥37 Weeks**", "<br>", "N = ", overall_age_n$`≥37 Weeks`),
    stat_0 ~ paste0("**Overall**", "<br>", "N = ", nrow(retro))) |> 
  modify_table_body(
    ~ .x |>
      dplyr::mutate(
        across(starts_with("stat_"), ~ stringr::str_replace_all(., "^0 \\(.*\\)$", "0")))) |> 
  as_gt() |>
  gt::tab_style(
    style = gt::cell_fill(color = "grey80"),
    locations = gt::cells_body(
      rows = c(1, 5, 9, 13, 17, 21, 25)))


postop_resp_tbl <- retro |> 
  mutate(po_dc_oxygen = case_when(
    po_rsp_oxy== 1 ~ "Yes",
    po_rsp_oxy== 0 ~ "No"),
    po_dc_oxygen = replace_na(po_dc_oxygen, "No"),
    resp_supp_free_days = case_when(
      ae_type == 1 ~ 0,
      po_rsp_oxy== 1 ~ 0,
      postop_resp_supp == "No" ~ hosp_los,
      postop_resp_supp == "Yes" ~ (hosp_los - resp_supp_dur_hrs)),
    resp_supp_free_days = resp_supp_free_days/24) |> 
  select(postop_resp_supp, resp_supp_change, resp_supp_type, resp_supp_dur_hrs, resp_supp_free_days, po_dc_oxygen, age_cat) |> 
  tbl_summary(by = age_cat, missing="no",
        label = list(
          postop_resp_supp = "Post-Operative Respiratory Support",
          resp_supp_change = "Change in Respiratory Support from Pre-Operative",
          resp_supp_type = "Post-Operative Respiratory Support Type",
          resp_supp_dur_hrs = "Post-Operative Respiratory Support Duration (Hrs)",
          po_dc_oxygen = "Discharge Home on Supplemental Oxygen",
          resp_supp_free_days = "Respiratory Support-Free Days")) |> 
  add_overall(last = FALSE) |> 
  bold_labels() |> 
  italicize_labels() |> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**")

# Plot Respiratory Support-Free Days
# Anaesthetic Type
rsfd_plot_overall <- rsfd_plot_fn(retro)
rsfd_plot_ga <- rsfd_plot_fn(retro, strata_var = "anaes_type", strata_value = "GA Only")
rsfd_plot_ga_spi <- rsfd_plot_fn(retro, strata_var = "anaes_type", strata_value = "GA + Spinal")
rsfd_plot_ga_caud <- rsfd_plot_fn(retro, strata_var = "anaes_type", strata_value = "GA + Caudal")
rsfd_plot_spi <- rsfd_plot_fn(retro, strata_var = "anaes_type", strata_value = "Spinal Only")
rsfd_plot_spi_sed <- rsfd_plot_fn(retro, strata_var = "anaes_type", strata_value = "Spinal + Sedation")
rsfd_plot_caud <- rsfd_plot_fn(retro, strata_var = "anaes_type", strata_value = "Caudal Only")
rsfd_plot_caud_sed <- rsfd_plot_fn(retro, strata_var = "anaes_type", strata_value = "Caudal + Sedation")

# Age Category
rsfd_plot_27 <- rsfd_plot_fn(retro, strata_var = "age_cat", strata_value = "≤ 27 Weeks")
rsfd_plot_28_32 <- rsfd_plot_fn(retro, strata_var = "age_cat", strata_value = "28-32 Weeks")
rsfd_plot_33_36 <- rsfd_plot_fn(retro, strata_var = "age_cat", strata_value = "33-36 Weeks")
rsfd_plot_37 <- rsfd_plot_fn(retro, strata_var = "age_cat", strata_value = "≥37 Weeks")


postop_outcome_tbl <- retro |> 
  select(disposition, disposition_change, hosp_los_days, hosp_readm, hosp_readm_reason, age_cat) |> 
  tbl_summary(by = age_cat, missing="no",
      label = list(
          disposition = "Post-Operative Disposition",
          disposition_change = "Change in Disposition Compared to Pre-Operatively",
          hosp_los_days = "Median Hospital LOS (Days)",
          hosp_readm = "Hospital Readmissions",
          hosp_readm_reason = "Hospital Readmission Reason")) |> 
  bold_labels() |> 
  italicize_labels() |> 
  add_overall(last = FALSE) |> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**")

```

### Post-Operative
#### Outcomes

::: panel-tabset
## Outcomes
```{r, message=FALSE, warning=FALSE, echo = F}
postop_outcome_tbl
```

## Analgesia
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_postop_analg
```

## Post-Operative Respiratory Support
```{r, message=FALSE, warning=FALSE, echo = F}
postop_resp_tbl
```
:::

#### Respiratory Support-Free Days
##### Anaesthetic Type
::: panel-tabset
## Overall
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_overall
```

## GA Only
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_ga
```

## GA + Spinal
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_ga_spi
```

## GA + Caudal
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_ga_caud
```

## Spinal Only
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_spi
```

## Spinal + Sedation
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_spi_sed
```

## Caudal Only
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_caud
```

## Caudal + Sedation
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_caud_sed
```
:::

##### Age Categories
::: panel-tabset
## ≤ 27 Weeks
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_27
```

## 28-32 Weeks
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_28_32
```

## 33-36 Weeks
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_33_36
```

## ≥37 Weeks
```{r, message=FALSE, warning=FALSE, echo = F}
rsfd_plot_37
```
:::


```{r, include=FALSE}
#==========================================TABLE 5: POST-OPERATIVE COMPLICATIONS==========================================#

# Postop Complicaation Numbers
tbl_overall_postop_compl <- tbl_compl_fn("All", intraop = FALSE)
tbl_ga_postop_compl <- tbl_compl_fn("GA Only", intraop = FALSE)
tbl_ga_caud_postop_compl <- tbl_compl_fn("GA + Caudal", intraop = FALSE)
tbl_ga_spi_postop_compl <- tbl_compl_fn("GA + Spinal", intraop = FALSE)
tbl_spi_postop_compl <- tbl_compl_fn("Spinal Only", intraop = FALSE)
tbl_spi_sed_postop_compl <- tbl_compl_fn("Spinal + Sedation", intraop = FALSE)
tbl_caud_postop_compl <- tbl_compl_fn("Caudal Only", intraop = FALSE)
tbl_caud_sed_postop_compl <- tbl_compl_fn("Caudal + Sedation", intraop = FALSE)

# Stack Tables
tbl_postop_compl <- tbl_stack(
  tbls = list(tbl_overall_postop_compl,tbl_ga_postop_compl, tbl_ga_caud_postop_compl, tbl_ga_spi_postop_compl, tbl_spi_postop_compl, tbl_spi_sed_postop_compl, tbl_caud_postop_compl, tbl_caud_sed_postop_compl)) |> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  modify_spanning_header(stat_0 ~ NA) |> 
  modify_footnote(everything() ~ NA) |> 
  modify_header(label ~ "**Anaesthetic Type**") |> 
  modify_table_body(
    ~ .x |>
      dplyr::mutate(
        across(starts_with("stat_"), ~ stringr::str_replace_all(., "^0 \\(.*\\)$", "0")))) |> 
  as_gt() |>
  gt::tab_style(
    style = gt::cell_fill(color = "grey80"),
    locations = gt::cells_body(rows = 1)) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(rows = 1))

# Complication Types per Anaesthetic Type
tbl_overall_postop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_postop_", 1:5),
  strata = "Overall",
  label = "Overall")

tbl_ga_postop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_postop_", 1:5),
  strata = "GA Only",
  label = "GA Only",
  add_n_to_label = TRUE)

tbl_ga_caud_postop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_postop_", 1:5),
  strata = "GA + Caudal",
  label = "GA + Caudal",
  add_n_to_label = TRUE)

tbl_ga_spi_postop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_postop_", 1:5),
  strata = "GA + Spinal",
  label = "GA + Spinal",
  add_n_to_label = TRUE)


tbl_spinal_postop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_postop_", 1:5),
  strata = "Spinal Only",
  label = "Spinal Only",
  add_n_to_label = TRUE)

tbl_spi_sed_postop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_postop_", 1:5),
  strata = "Spinal + Sedation",
  label = "Spinal + Sedation",
  add_n_to_label = TRUE)

# No Caudal Only 

tbl_caud_sed_postop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("complication_type_postop_", 1:5),
  strata = "Caudal + Sedation",
  label = "Caudal + Sedation",
  add_n_to_label = TRUE)

# Stack Tables
tbl_postop_compl_type <- tbl_stack(
  tbls = list(tbl_overall_postop_compl, tbl_ga_postop_compl, tbl_ga_caud_postop_compl, tbl_ga_spi_postop_compl, tbl_spinal_postop_compl, tbl_spi_sed_postop_compl, tbl_caud_sed_intraop_compl)) |> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  modify_spanning_header(stat_0 ~ NA) |> 
  modify_footnote(everything() ~ NA) |> 
  modify_header(
    label ~ "**Anaesthetic Type**",
    stat_1 ~ paste0("**≤ 27 Weeks**", "<br>", "N = ", overall_age_n$`≤ 27 Weeks`),
    stat_2 ~ paste0("**28-32 Weeks**", "<br>", "N = ", overall_age_n$`28-32 Weeks`),
    stat_3 ~ paste0("**33-36 Weeks**", "<br>", "N = ", overall_age_n$`33-36 Weeks`),
    stat_4 ~ paste0("**≥37 Weeks**", "<br>", "N = ", overall_age_n$`≥37 Weeks`),
    stat_0 ~ paste0("**Overall**", "<br>", "N = ", nrow(retro))) |> 
  as_gt() |>
  gt::tab_style(
    style = gt::cell_fill(color = "grey80"),
    locations = gt::cells_body(
      rows = c(1, 11, 17, 24, 26, 33, 35)))


# Postop Complication Timing
tbl_postop_compl_timing_overall <- tbl_complication_timing(retro, strata = "Overall")
tbl_postop_compl_timing_ga <- tbl_complication_timing(retro, strata = "GA Only")
tbl_postop_compl_timing_ga_caud <- tbl_complication_timing(retro, strata = "GA + Caudal")
tbl_postop_compl_timing_ga_spi <- tbl_complication_timing(retro, strata = "GA + Spinal")
tbl_postop_compl_timing_spinal <- tbl_complication_timing(retro, strata = "Spinal Only")
tbl_postop_compl_timing_spi_sed <- tbl_complication_timing(retro, strata = "Spinal + Sedation")
# Caudal Only- no complications
tbl_postop_compl_timing_caud_sed <- tbl_complication_timing(retro, strata = "Caudal + Sedation")

# Complication Interventions
# Generate Overall Row
tbl_overall_postop_compl_int <- tbl_overall_postop_compl |> 
  remove_row_type(complication_type, type = "level")

# By Complication Type
tbl_brady_postop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("brd_int_postop_", 1:5),
  strata = "Overall",
  label = "Bradycardia",
  intervention = TRUE)

# Hypotension- no intervention

tbl_apn_postop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("apn_int_postop_", 1:5),
  strata = "Overall",
  label = "Apnoea",
  intervention = TRUE)

tbl_des_postop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("des_int_postop_", 1:5),
  strata = "Overall",
  label = "Desaturation",
  intervention = TRUE)

# Bronchospasm- no intervention

tbl_lar_postop_compl <- tbl_complication_types_fn(
  complication_cols = paste0("lar_int_postop_", 1:5),
  strata = "Overall",
  label = "Laryngospasm",
  intervention = TRUE)

# Stack Tables
tbl_postop_compl_int <- tbl_stack(
  tbls = list(tbl_overall_postop_compl_int, tbl_brady_postop_compl, tbl_apn_postop_compl, tbl_des_postop_compl, tbl_lar_postop_compl), quiet = TRUE) |> 
  modify_spanning_header(all_stat_cols() ~ "**Age Categories at Birth**") |> 
  modify_spanning_header(stat_0 ~ NA) |> 
  modify_footnote(everything() ~ NA) |> 
  modify_header(
    label ~ "**Complication Type & Intervention**",
    stat_1 ~ paste0("**≤ 27 Weeks**", "<br>", "N = ", overall_age_n$`≤ 27 Weeks`),
    stat_2 ~ paste0("**28-32 Weeks**", "<br>", "N = ", overall_age_n$`28-32 Weeks`),
    stat_3 ~ paste0("**33-36 Weeks**", "<br>", "N = ", overall_age_n$`33-36 Weeks`),
    stat_4 ~ paste0("**≥37 Weeks**", "<br>", "N = ", overall_age_n$`≥37 Weeks`),
    stat_0 ~ paste0("**Overall**", "<br>", "N = ", nrow(retro))) |> 
  as_gt() |>
  gt::tab_style(
    style = gt::cell_fill(color = "grey75"),
    locations = gt::cells_body(
      rows = c(1))) |> 
  gt::tab_style(
    style = gt::cell_fill(color = "grey90"),
    locations = gt::cells_body(
      rows = c(2, 9, 16, 30)))

```


#### Complications
Overall, there were 87 patients that had a post-operative complication, with 129 post-operative complication events.

::: panel-tabset
## Number of Complications
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_postop_compl
```

## Complication Type
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_postop_compl_type
```

## Intervention
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_postop_compl_int
```
:::

#### Complication Timing

::: panel-tabset
## Overall
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_postop_compl_timing_overall
```

## GA
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_postop_compl_timing_ga
```

## GA + Caudal
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_postop_compl_timing_ga_caud
```

## GA + Spinal
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_postop_compl_timing_ga_spi
```

## Spinal Only
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_postop_compl_timing_spinal
```

## Spinal + Sedation
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_postop_compl_timing_spi_sed
```

## Caudal + Sedation
```{r, message=FALSE, warning=FALSE, echo = F}
tbl_postop_compl_timing_caud_sed
```
:::


```{r, include=FALSE}
#==========================================TABLE 6: ADVERSE EVENTS==========================================#

retro_adverse_tbl <- retro |> 
  filter(!is.na(adverse_timepoint)) |> 
  select(age_cat, adverse_timepoint, adverse_type) |> 
  arrange(age_cat) |> 
  gt(groupname_col= "adverse_timepoint") |> 
  tab_options(row_group.as_column = T) |> 
  row_group_order(groups = c("Pre-Operative", "Intra-Operative", "Post-Operative")) |> 
  cols_label(
    age_cat = md("**Age Category**"),
    adverse_type = md("**Adverse Event Type**"))

```

### Adverse Events
There were 7 adverse events in the entire cohort.
```{r, message=FALSE, warning=FALSE, echo = F}
retro_adverse_tbl
```

